NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-07-24 paper/Chapters/Chapter2.tex
strata and weighting

\begin{itemize}
	\item Total Energy intake = (protein(gram) $\times$ 17) + (fat(gram) $\times$ 37) + (carbohydrate(gram) $\times$ 16) + (alcohol(gram) $\times$ 29)  kJ;
	\item Carbohydrate intake = total sugars (gram) + starch (gram); 
	\item Total sugars = sum of all individual sugars (gram).
\end{itemize}

@@

\begin{itemize}
	\item Not eating; 
	\item Eating, and carbohydrate contributed less than 50\% of the total energy intake;
	\item Eating, and carbohydrate contributed higher or equal to 50\% of the total energy intake.
\end{itemize}

@@

\section{Latent Class Growth Analysis (LCGA)}

\section{Survey Data}

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Survey Selection Method}

The NDNS RP participants were drawn from the UK Postcode Address File, a list of all the addresses in the UK. The addresses were clustered into Primary Sampling Units (PSUs)

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------
\subsection{Response rates}

>>>>

\begin{itemize}
	\item Total Energy intake = (protein(gramme) $\times$ 17) + (fat(gramme) $\times$ 37) + (carbohydrate(gramme) $\times$ 16) + (alcohol(gramme) $\times$ 29)  kJ;
	\item Carbohydrate intake = total sugars (gramme) + starch (gramme); 
%	\item Total sugars = sum of all individual sugars (gramme).
\end{itemize}

@@

\begin{itemize}
	\item Not eating any food; 
	\item Eating, and carbohydrate contributed less than 50\% of the total energy intake;
	\item Eating, and carbohydrate contributed higher or equal to 50\% of the total energy intake.
\end{itemize}
\vspace{-0.5cm}

\section{Survey Data}\vspace{-0.3cm}

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Survey Selection Method}\vspace{-0.3cm}

The NDNS RP participants were drawn from the UK Postcode Address File, a list of all the addresses in the UK. The addresses were clustered into Primary Sampling Units (PSUs), small geographical areas, based on postcode sectors, randomly selected from across the UK. A list of 27 or 28 addresses was then randomly selected from each PSU.

Overall, for years 1 to 8 combined, a sample of 39,300 address was selected from 1,438 PSUs. The sampling selection process was:

\begin{itemize}
	\item Randomly select PSUs from the Postcode Address File; 
	\item Randomly select 27 or 28 addresses in that postcode area; 
	\item Randomly select one household at that address; 
	\item Selected addresses were randomly allocated to one of two groups to determine whether an adult (aged 19 years or older) and a child (aged 1.5 to 18 years), or a child only, were selected for interview.
\end{itemize}
\vspace{-0.6cm}
%-----------------------------------
%	SUBSECTION 2
%-----------------------------------
\subsection{Response rates}\vspace{-0.3cm}

The response rates for completion of the food diary (three or four days) were 56\%, 53\%, 53\%, for years 1 to 4 combined, 5 to 6 combined and 7 to 8 combined, respectively. A total of 6,155 adults aged 19 years and over were kept in our analysis. 
\vspace{-1.2cm}

\subsection{Strata and weightings}\vspace{-0.3cm}

The strata that used to calibrate proportions in the sample include: age-group (1.5-3, 4-6, 7-10, 11-15, 16-18, 19-24, 25-29, 30-39, 40-49, 50-59, 60-64, 65-69, and over 70 years); sex (men or women); and regions (Northern Ireland, Scotland, Wales, and the nine regions of England).

It is necessary to apply weighting factors to the data collected in the NDNS RP for two reasons: to remove any bias in the observed results which may be due to differences in the probability of households and individuals being selected to take part; and to attempt to reduce differential non-response bias by age, sex and geographical region.

@@

\section{Latent Class Growth Analysis (LCGA)}\vspace{-0.3cm}
